Papers I Love

### 2018-01-01 texts/dev/PapersILove.tex
monadic task for c# (maybe) working with async await
calculus limit proof
.
fundamentals of matrix computations exercises

\subsubsection{Distributed Systems}
\begin{enumerate}
	\item {Time, Clocks and the Ordering of Events in a Distributed System\\		
\href{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#time-clocks}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#time-clocks}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}}
	\item {Distributed Snapshots: Determining Global States of Distributed Systems\\
\href{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#chandy}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#chandy}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}}
	\item {Your Coffee Shop Doesn’t Use Two-Phase Commit\\
\href{http://www.enterpriseintegrationpatterns.com/docs/IEEE_Software_Design_2PC.pdf}{http://www.enterpriseintegrationpatterns.com/docs/IEEE\_Software\_Design\_2PC.pdf}}
	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
\url{http://www.ics.uci.edu/~cs223/papers/cidr07p15.pdf}}
\end{enumerate}

@@

\subsection{Programming Paradigms}
\subsubsection{Language Analysis}
\begin{enumerate}
	\item {Evaluating the Design of the R Language\\ \url{http://r.cs.purdue.edu/pub/ecoop12.pdf}}
\end{enumerate}
\subsubsection{Process Theory}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
\end{enumerate}
\subsubsection{Object Oriented}
\begin{enumerate}
	\item {A Theory of Objects\\
\url{http://academic.research.microsoft.com/Publication/1354440/a-theory-of-objects}\\
\url{http://lucacardelli.name/Talks/1997-06\%20A\%20Theory\%20of\%20Object\%20(ECOOP\%20Tutorial).pdf}}
	\item {Traits: Composable Units of Behaviour\\
\url{http://scg.unibe.ch/archive/papers/Scha03aTraits.pdf}}
	\item {Applying Traits to the Smalltalk Collection Hierarchy\\
\url{http://www.researchgate.net/publication/2564879_Applying_Traits_to_the_Smalltalk_Collection_Hierarchy}}
	\item {A Laboratory for Teaching Object-Oriented Thinking\\
\url{http://www.inf.ed.ac.uk/teaching/courses/seoc/2007_2008/resources/CRC_OOthinking.pdf}}
\end{enumerate}

\subsubsection{Generic Programming}
	\begin{enumerate}
	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.html}}
	\end{enumerate}
\subsubsection{Dynamic Dispatch}
\subsubsection{Functional Programming}
\begin{enumerate}
	\item {Monadic Parser Combinators\\
\url{http://www.cs.nott.ac.uk/~pszgmh/monparsing.pdf}}
\end{enumerate}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Linear Algebra}
\begin{enumerate}
	\item {Basic Linear Algebra Subprograms for Fortran Usage\\
\url{https://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/19780018835.pdf}}
	\item{FLAME: Formal Linear Algebra Methods Environment\\
\url{http://tinyurl.com/ycxkmzw7}}
	\item{The Five Greatest Applications of Markov Chains\\
\url{http://langvillea.people.cofc.edu/MCapps7.pdf}}
\end{enumerate}
\subsection{Real Analysis}
\begin{enumerate}
	\item {Coisas que o Luís precisa aprender\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE
	\url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
	\item{Data Mining and Statistics: What's the Connection\\ \url{http://docs.salford-systems.com/dm-stat.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}

>>>>

\subsubsection{Distributed Systems}
\begin{enumerate}
	\item {Time, Clocks and the Ordering of Events in a Distributed System\\		
\href{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}{http://academic.research.microsoft.com/Publication/775212/time-clocks-and-the-ordering-of-events-in-a-distributed-system}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#time-clocks}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#time-clocks}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/time-clocks.pdf}}
	\item {Paxos Made Simple\\
	\url{https://www.microsoft.com/en-us/research/publication/paxos-made-simple/}}
	\item {Distributed Snapshots: Determining Global States of Distributed Systems\\
\href{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}{http://academic.research.microsoft.com/Publication/803548/distributed-snapshots-determining-global-states-of-distributed-systems}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html#chandy}{http://research.microsoft.com/en-us/um/people/lamport/pubs/pubs.html\#chandy}\\
\href{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}{http://research.microsoft.com/en-us/um/people/lamport/pubs/chandy.pdf}}
	\item {Your Coffee Shop Doesn’t Use Two-Phase Commit\\
\href{http://www.enterpriseintegrationpatterns.com/docs/IEEE_Software_Design_2PC.pdf}{http://www.enterpriseintegrationpatterns.com/docs/IEEE\_Software\_Design\_2PC.pdf}}
	\item {Life Beyond Distributed Transactions: An Apostate’s Opinion\\
\url{http://www-db.cs.wisc.edu/cidr/cidr2007/papers/cidr07p15.pdf}}
\end{enumerate}

@@

\subsection{Programming Paradigms}
\subsubsection{Language Analysis}
\begin{enumerate}
	\item {Evaluating the Design of the R Language\\ \url{http://r.cs.purdue.edu/pub/ecoop12.pdf}}
\end{enumerate}
\subsubsection{Process Theory}
\begin{enumerate}
	\item {A Brief History of Process Algebra\\
\url{http://alexandria.tue.nl/extra1/wskrap/publichtml/200402.pdf}}
\end{enumerate}
\subsubsection{Object Oriented}
\begin{enumerate}
	\item {A Theory of Objects\\
\url{http://academic.research.microsoft.com/Publication/1354440/a-theory-of-objects}\\
\url{http://lucacardelli.name/Talks/1997-06\%20A\%20Theory\%20of\%20Object\%20(ECOOP\%20Tutorial).pdf}}
	\item {Traits: Composable Units of Behaviour\\
\url{http://scg.unibe.ch/archive/papers/Scha03aTraits.pdf}}
	\item {Applying Traits to the Smalltalk Collection Hierarchy\\
\url{http://www.researchgate.net/publication/2564879_Applying_Traits_to_the_Smalltalk_Collection_Hierarchy}}
	\item {A Laboratory for Teaching Object-Oriented Thinking\\
\url{http://www.inf.ed.ac.uk/teaching/courses/seoc/2007_2008/resources/CRC_OOthinking.pdf}}
\end{enumerate}
\subsubsection{Generic Programming}
	\begin{enumerate}
	\item {Design Patterns for Generic Programming in C++\\ \url{https://www.lrde.epita.fr/dload/papers/coots01.html}}
	\end{enumerate}
\subsubsection{Dynamic Dispatch}
\subsubsection{Functional Programming}
\begin{enumerate}
	\item{The essence of functional programming \\
\url{http://homepages.inf.ed.ac.uk/wadler/papers/essence/essence.ps.gz}}
	\item {Monadic Parser Combinators\\
\url{http://www.cs.nott.ac.uk/~pszgmh/monparsing.pdf}}
\end{enumerate}
\begin{enumerate}
	\item {Design and evaluation of C++ open multi-methods\\
\url{https://parasol.tamu.edu/~yuriys/papers/OMM10.pdf}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Geometry}
\begin{enumerate}
	\item {An Elementary Course in Synthetic Projective Geometry}
\end{enumerate}
\subsection{Linear Algebra}
\begin{enumerate}
	\item {Basic Linear Algebra Subprograms for Fortran Usage\\
\url{https://ntrs.nasa.gov/archive/nasa/casi.ntrs.nasa.gov/19780018835.pdf}}
	\item{FLAME: Formal Linear Algebra Methods Environment\\
\url{http://tinyurl.com/ycxkmzw7}}
	\item{The Five Greatest Applications of Markov Chains\\
\url{http://langvillea.people.cofc.edu/MCapps7.pdf}}
\end{enumerate}
\subsection{Real Analysis}
\begin{enumerate}
	\item {Coisas que o Luís precisa aprender\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE
	\url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
	\item{Data Mining and Statistics: What's the Connection\\ \url{http://docs.salford-systems.com/dm-stat.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}
